Invertible Resnets up to Homology Equivalence for Connected Abelian Lie Groups

### 2020-04-04 llncs2e/paper77.tex
error

\section{Conclusions}
\label{sec:conclusion}
Based on the theory of Lie groups and persistent homology a method for invertible resnets was developed to parameterize them with good precision due to the assumption that the data lies on or near by some commutative Lie group. This forms an approximate solution for a special case of learning problems, allowing to restrict the domain to a commutative group. The initial problem could be simplified by decomposing the Lie group into a product space $\mathbb{R}^p \times \mathbb{T}^q$. The homology groups of the $q$-torus and the Euclidean space are well known. The application of fully invertible neural nets to resnets demonstrates our results on a different Lie group from Euclidean space. By applying Künneth's theorem the homology groups of the topological factor spaces could be connected with the ones of their product space. Using mean confident persistence landscapes the homology groups were estimated. A treshold was computed, see sect. \ref{sec:numericalexperiments}, which is determined by the state space dimension of the resets according to a representation up to homology equivalence. The mean persistence landscapes are particularly useful for short-lived isolated collections of data points, which in particular generate elements from homology classes at the beginning of the filtering and become visible at the lower left corner of the persistence landscapes, see Fig. \ref{homgroups} (a). The theoretical work was tested with numerical experiments on toy data. We do not limit the processing of the neural net within the layers to an abelian group. Instead, we assume that the net learns this structure from the input domain. This seems to hold, according to our experiments. Still, it can cause inaccuracies in the estimation of the dimensional treshold. The abelianization of the invertible layers would solve this problem.

>>>>

\section{Conclusions}
\label{sec:conclusion}
Based on the theory of Lie groups and persistent homology a method for invertible resnets was developed to parameterize them with good precision due to the assumption that the data lies on or near by some connected commutative Lie group. This forms an approximate solution for a special case of learning problems, allowing to restrict the domain to a commutative group. The initial problem could be simplified by decomposing the Lie group into a product space $\mathbb{R}^p \times \mathbb{T}^q$. The homology groups of the $q$-torus and the Euclidean space are well known. The application of fully invertible neural nets to resnets demonstrates our results on a different Lie group from Euclidean space. By applying Künneth's theorem the homology groups of the topological factor spaces could be connected with the ones of their product space. Using mean confident persistence landscapes the homology groups were estimated. A treshold was computed, see sect. \ref{sec:numericalexperiments}, which is determined by the state space dimension of the resets according to a representation up to homology equivalence. The mean persistence landscapes are particularly useful for short-lived isolated collections of data points, which in particular generate elements from homology classes at the beginning of the filtering and become visible at the lower left corner of the persistence landscapes, see Fig. \ref{homgroups} (a). The theoretical work was tested with numerical experiments on toy data. We do not limit the processing of the neural net within the layers to an abelian group. Instead, we assume that the net learns this structure from the input domain. This seems to hold, according to our experiments. Still, it can cause inaccuracies in the estimation of the dimensional treshold. The abelianization of the invertible layers would solve this problem.
